Incentivizing Exploration with Unbiased History

### 2018-10-28 3level.tex
some appendix edits

\subsection{Events}
We will first establish four \nidelete{\emph{clean events}} \niedit{events} \nicomment{this is a dumb name, what's clean or dirty about an event?  i advocate deleting this adjective from our paper, as i did for the 2level section} that together occur
with probability at least $1 - O(1/T)$. The first event says that
every group of \ALGG runs in the first level ensures that each arm $a$
is pulled at least $\Omega(T_1)$ times. The following lemma can
derived from combining Lemma~\ref{lem:t1runs} and union bound.

@@

Finally, consider the \emph{small gap} case where $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(S T_1))})$. This
is more challenging since even aggregating the data from all $S$
groups in the first level is not sufficient for correctly
distinguishing the two arms. Thus, we need to ensure that both arms
will continue to be pulled in the second level. To achieve this, we
will nicely leverage the event of $W_4$, which has the implication
that each arm $a$ has a ``lucky'' group $s_a$ in the first level,
for which its empirical mean is slightly higher than $\mu_a$, while
the other arm is slightly lower than $\mu_{(3-a)}$. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, the sub-history
from this ``lucky'' group will induce a pair of estimates such that
$\hat \mu_a^t > \hat \mu_{(3-a)}^t$, and so any second-level agent in
group $s_a$ will pull arm $a$.  As a result, we guarantee both arms
will be pulled at least $T_2$ times in the second level, which in turn
gives the following guarantee.

>>>>

\subsection{Events}
We will first establish four events that together occur
with probability at least $1 - O(1/T)$. The first event says that
every group of \ALGG runs in the first level ensures that each arm $a$
is pulled at least $\Omega(T_1)$ times. The following lemma can
derived from combining Lemma~\ref{lem:t1runs} and union bound.

@@

Finally, consider the \emph{small gap} case where $\Delta$ is between
$\tilde\Omega(\sqrt{1/T_2})$ and $\tilde O(\sqrt{1/(S T_1))})$. This
is more challenging since even aggregating the data from all $S$
groups in the first level is not sufficient for correctly
distinguishing the two arms. Thus, we need to ensure that both arms
will continue to be pulled in the second level. To achieve this, we
will nicely leverage the event of $W_4$, which has the implication
that each arm $a$ has a ``lucky'' group $s_a$ in the first level,
for which its empirical mean is slightly higher than $\mu_a$, while
the other arm is slightly lower than $\mu_{(3-a)}$. Since the
deviations are in the order of $\Omega(\sqrt{1/T_1})$, and Assumption~\ref{ass:embehave} guarantees the estimates are also within $\Omega(\sqrt{1/T_1})$ of the empirical means, the sub-history
from this ``lucky'' group will yield estimates such that
$\hat \mu_a^t > \hat \mu_{(3-a)}^t$, and so any second-level agent in
group $s_a$ will pull arm $a$.  As a result, we guarantee both arms
will be pulled at least $T_2$ times in the second level, which in turn
gives the following guarantee.
